Codebook
========
Codebook was generated on `r as.character(Sys.time())` during the run_analysis.R script execution.

Variable list and descriptions
------------------------------

Variable name    | Description
-----------------|------------
subject          | ID of the subject who performed the activity for each window sample
activity         | Activity name
featDomain       | Feature - Time domain signal or frequency domain signal (Time or Freq)
featInstrument   | Feature - Measuring instrument (Accelerometer or Gyroscope)
featAcceleration | Feature - Acceleration signal (Body or Gravity)
featVariable     | Feature - Variable (Mean or SD)
featJerk         | Feature - Jerk signal
featMagnitude    | Feature - Magnitude of the signals calculated using Euclidean norm
featAxis         | Feature - 3-axial signals in the X, Y and Z directions (X, Y, or Z)
featCount        | Feature - Count of data points used to compute average
featAverage      | Feature - Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r}
str(dtTidy)
```

List the key variables in the data table
----------------------------------------

```{r}
key(dtTidy)
```

Sample dataset rows
------------------------------

```{r}
dtTidy
```

Summary of variables
--------------------

```{r}
summary(dtTidy)
```

All possible combinations of features
------------------------------------------

```{r}
dtTidy[, .N, by=c(names(dtTidy)[grep("^feat", names(dtTidy))])]
```


